OmniVisor - OmniScale Hypervisor for Disaggregated Architecture

### 2019-11-03 paper.tex
Cleanup citation using LaTeX's cited function.

The datacenter systems have used server-centric architecture for many years where the hardware resources are tightly integrated within one machine. There are some limits on the server-centric architecture including under-utilized resources, weak support for heterogeneous computing, poor failure handling, and hard to achieve hardware resource elasticity. The resource disaggregation architecture is then proposed to tackle these limits. There are some disaggregated architecture proposals include Intel’s Rack Scale Architecture[1], HP’s “The Machine”[2], Facebook’s Disaggregated Rack[3], and IBM’s Composable System[4]. The key enabling factor of the disaggregated architecture is network techniques that whether network performance can meet the performance requirement of bus-connected processors and memory[5]. There are some network techniques enable the possibility of the disaggregated architecture: the high-speed and more scalable network techniques such as RDMA[6], InfiniteBand[7], and new network stack for rack-scale computers[8]; network hardware devices accessing without the need of attaching to processors[9, 10]. \par
    As for the software sides to manage resources on disaggregated architecture, there are some techniques to target specific types of resources. Support disaggregated memory with transparently access through processor’s memory instructions[11, 12]. Another challenging point to resource disaggregation is how to separate memory from processors as most of the architecture have tightly-coupled processors and memory. Moreover, there are also instructions carrying out memory access. LegoOS[18] emulates the separation of processor and memory by trapping all memory accesses, excluding cache access, and redirect them to access remote memory via page fault handler. As for storage management, accessing the remote disks is already a common practice [13, 14]. \par
    For operating systems, there are some previous works to manage the distributed resource across multiple machines. Ameoba OS[15, 16] and fos[17] builds a single image microkernel-based OS to run across multiple physical machines, for example, supporting Infrastructure as a Service (IaaS) in the cloud computing context. The motivation is to release application developers from the complexity of resources management. Having many machines to form a huge resource pool, users should be able to use the resources without considering managing them across machines or worry about the location of machines. For example, in the cloud computing context, developers don’t need to consider how many resources and VMs are required for a certain task. \par

@@

    LegoOS[18] is a prototype operating system specifically targeting on disaggregated architecture. It proposes a splitkernel OS architecture that split the kernel functionalities into several services. As the hardware resources are separate, the managing software is also split. Each service manages its own hardware component and communicates with each other via network. For instance, there are different software components to manage processors, memory, and storage hardware individually. But same as Ameoba OS and fos, LogoOS design a completely new OS and therefore is weak in backward compatibility and lack of flexibility for users to choose different OSes to use. \par

@@

\subsection{Target Architecture}
For disaggregated architecture, all hardware computing resources such as processors, memory, and storage are separately located. Though processors and memory are separate, we assume there are still a few amount of memory stay with the processors. This assumption is reasonable given the network speed still not catches on the processor-memory performance requirement\cite{NetworkRequirement} and datacenter applications usually show great temporal data locality\cite{NNLoad,MapReduceLoad}. So in this paper, the memory components in our target architecture include local and remote memory as depicted in Fig \ref{fig:disaggregated architecture}.

>>>>

The datacenter systems have used server-centric architecture for many years where the hardware resources are tightly integrated within one machine. There are some limits on the server-centric architecture including under-utilized resources, weak support for heterogeneous computing, poor failure handling, and hard to achieve hardware resource elasticity. The resource disaggregation architecture is then proposed to tackle these limits. There are some disaggregated architecture proposals include Intel’s Rack Scale Architecture\cite{Intel_RSA}, HP’s “The Machine”\cite{HP_The_Machine}, Facebook’s Disaggregated Rack\cite{FB_disaggregated_rack}, and IBM’s Composable System\cite{IBM_composable_system}. The key enabling factor of the disaggregated architecture is network techniques that whether network performance can meet the performance requirement of bus-connected processors and memory\cite{Network_requirement}. There are some network techniques enable the possibility of the disaggregated architecture: the high-speed and more scalable network techniques such as RDMA\cite{RDMA}, InfiniteBand\cite{InfiniteBand}, and new network stack for rack-scale computers\cite{Network_stack_for_rack}; network hardware devices accessing without the need of attaching to processors\cite{NVM_performance, NVM_performance2}. \par
    As for the software sides to manage resources on disaggregated architecture, there are some techniques to target specific types of resources. Support disaggregated memory with transparently access through processor’s memory instructions\cite{Disaggregated_memory, Disaggregated_memory2}. Another challenging point to resource disaggregation is how to separate memory from processors as most of the architecture have tightly-coupled processors and memory. Moreover, there are also instructions carrying out memory access. LegoOS[18] emulates the separation of processor and memory by trapping all memory accesses, excluding cache access, and redirect them to access remote memory via page fault handler. As for storage management, accessing the remote disks is already a common practice\cite{VMware_virtual_SAN, Amazon_EC2_root_volume}. \par
    For operating systems, there are some previous works to manage the distributed resource across multiple machines. Ameoba OS\cite{Amoeba_OS} and fos\cite{fos} builds a single image microkernel-based OS to run across multiple physical machines, for example, supporting Infrastructure as a Service (IaaS) in the cloud computing context. The motivation is to release application developers from the complexity of resources management. Having many machines to form a huge resource pool, users should be able to use the resources without considering managing them across machines or worry about the location of machines. For example, in the cloud computing context, developers don’t need to consider how many resources and VMs are required for a certain task. \par

@@

    LegoOS\cite{LegoOS} is a prototype operating system specifically targeting on disaggregated architecture. It proposes a splitkernel OS architecture that split the kernel functionalities into several services. As the hardware resources are separate, the managing software is also split. Each service manages its own hardware component and communicates with each other via network. For instance, there are different software components to manage processors, memory, and storage hardware individually. But same as Ameoba OS and fos, LogoOS design a completely new OS and therefore is weak in backward compatibility and lack of flexibility for users to choose different OSes to use. \par

@@

\subsection{Target Architecture}
For disaggregated architecture, all hardware computing resources such as processors, memory, and storage are separately located. Though processors and memory are separate, we assume there are still a few amount of memory stay with the processors. This assumption is reasonable given the network speed still not catches on the processor-memory performance requirement\cite{Network_requirement} and datacenter applications usually show great temporal data locality\cite{NN_load,MapReduce_load}. So in this paper, the memory components in our target architecture include local and remote memory as depicted in Fig \ref{fig:disaggregated architecture}.
